The Astropy Project

### 2017-10-04 main.tex
Remove colon from title
Update on Overleaf.

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
% TODO: Do we want to put in a PDF of the transform graph?

\subsubsection{Overview}
The \texttt{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \texttt{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as a spherical (distance,
right ascension, declination) or Cartesian coordinates.
They can therefore be re-represented or transformed to other reference frames
(e.g., the Galactic frame) in an independent way.

The classes that handle coordinate representations (the \texttt{Representation}
classes) act like three-dimensional vectors and thus support vector arithmetic.
The classes that represent reference systems and frames (the \texttt{Frame}
classes) internally use \texttt{Representation} objects to store the coordinate
data---that is, the \texttt{Frame} classes accept coordinate data, either as a
specified \texttt{Representation} object, or using short-hand keyword arguments
to specify the components of the coordinates.
These preferred representation and short-hand component names differ between
various astronomical reference systems.
For example, in the ICRS frame, longitude and latitude are right ascension
(\texttt{ra}) and declination (\texttt{dec}), whereas in the Galactic frame, the
spherical angles are Galactic longitude (\texttt{l}) and latitude (\texttt{b}).
Each of the \texttt{Frame} classes define their own component names and
preferred \texttt{Representation} class.
The frame-specific component names map to corresponding components on the
underlying \texttt{Representation} object that internally stores the coordinate
data.
For most frames the preferred representation is spherical.

@@

\begin{description}
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg\ now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \texttt{astroplan} (TODO: cite zenodo entry?).

@@

    \item[JPL ephemeris]
    TODO: JPL ephemerids % Erik?
\end{description}

@@

>>>>

\subsection{Coordinates}
\label{sec:coordinates}
% Adrian, Erik
\inlinecomment{APW}{Do we want to put in a PDF of the transform graph?}
\inlinecomment{EJT}{I think so?  It looks pretty slick...}

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects. Some of the machinery also relies on the Essential Routines of Fundamental Astronomy (ERFA) C library for some of the critical underlying transformation machinery.
\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as spherical (right ascension, declination, and distance from solar system barycenter) or Cartesian coordinates ($x$, $y$, $z$ with the origin at ).
They can therefore change representations independent of being transformed to other reference frames (e.g., the Galactic coordinate frame).

The classes that handle coordinate representations (the \texttt{Representation}
classes) act like three-dimensional vectors and thus support vector arithmetic.
The classes that represent reference systems and frames (the \texttt{Frame}
classes) internally use \texttt{Representation} objects to store the coordinate
data---that is, the \texttt{Frame} classes accept coordinate data, either as a
specified \texttt{Representation} object, or using short-hand keyword arguments
to specify the components of the coordinates.
These preferred representation and short-hand component names differ between
various astronomical reference systems.
For example, in the ICRS frame, longitude and latitude are right ascension
(\texttt{ra}) and declination (\texttt{dec}), whereas in the Galactic frame, the
spherical angles are Galactic longitude (\texttt{l}) and latitude (\texttt{b}).
Each of the \texttt{Frame} classes define their own component names and
preferred \texttt{Representation} class.
The frame-specific component names map to corresponding components on the
underlying \texttt{Representation} object that internally stores the coordinate
data.
For most frames the preferred representation is spherical, although this is determined primarily by the common use in the astronomical community.

@@

\begin{description}
    \item[Local Earth coordinate frames] In addition to representing celestial
    coordinates, \astropypkg\ now supports specifying positions on the Earth in
    a number of different geocentric systems with the \texttt{EarthLocation}
    class.
    With this, \astropypkg\ now supports Earth-location-specific coordinate
    systems such as the altitude-azimuth (\texttt{AltAz}) or horizontal system.
    Transformations between \texttt{AltAz} and any Barycentric coordinate frame
    also requires specifying a time using the \texttt{Time} class from
    \texttt{astropy.time}.
    With this new functionality, many of the common tasks associated with
    observation planning can now be completed with \astropypkg\ or the
    \astropy-affiliated package \package{astroplan}. \inlinecomment{APW}{TODO: cite zenodo entry for astroplan?}.

@@

    \item[Solar System Ephemerides]
    \comment{EJT}{APW, you may want to give this item a quick read-over?  If it looks good just delete this comment}
    Also new is support for computing ephemeris of major solar system bodies and outputting the resulting positions as coordinate objects. 
    These ephemerides can be computed either using analytic approximations from ERFA (which requires no data download beyond the source code), or from downloaded JPL ephemerides (which requires the \package{jplephem}\footnote{\url{https://github.com/brandon-rhodes/python-jplephem}} optional dependency). 
    The \texttt{get\_body} and \texttt{get\_body\_barycentric} functions provide the gateway to this functionality, yielding \texttt{SkyCoord} objects given a specific body and choice of ephemeris source.

\end{description}

@@

\inlinecomment{EJT}{ERFA is likely to be referenced somewhere here. should cite the DOI as mentioned in the above ERFA refernce once it exists}
